Microlensing as a possible probe of event-horizon structure in quasars

### 2017-10-10 paper1/ms.tex
ready to resubmit

Figure \ref{fig:cc_backward} attempts a somewhat more realistic
situation.  The mock lightcurve is the same as before, but the
templates come from taking a crescent source along the path AB in
Figure~\ref{fig:magnification_map}.  That is, the mock data and the
templates come from crossings of different caustics.  This is intended
to mimic the systematic errors arising from not knowing the caustic
exactly.  As Figure~\ref{fig:cc_backward} shows, the fit is slightly
degraded, but still acceptable.  The parameters $r_{1/2}/v_p$ and
$R_n/R_p$ are still recovered.  The parameters $a/R_p$ and $b/R_p$
(not shown in the Figure) giving the orientation of the crescent were
not correctly recovered; but this is understandable, because the AB
and CB tracks have different orientations with respect to the caustics
crossed.  The slight degradation of the fit can be understood as
follows.  Although the caustics are clean folds, they have some
curvature, and moreover the curvature is not identical in the two
caustics used for the mock data and the template.

>>>>

Figure \ref{fig:cc_backward} attempts a somewhat more realistic
situation.  The mock lightcurve is the same as before, but the
templates come from taking a crescent source along the path AB in
Figure~\ref{fig:magnification_map}.  That is, the mock data and the
templates come from crossings of different caustics.  This is intended
to mimic the systematic errors arising from not knowing the caustic
exactly.  As Figure~\ref{fig:cc_backward} shows, the fit is slightly
degraded, but still acceptable.  The parameters $r_{1/2}/v_p$ and
$R_n/R_p$ are still recovered.  The parameters $a/R_p$ and $b/R_p$
(not shown in the Figure) giving the orientation of the crescent were
not correctly recovered; but this expected, because the AB and CB
tracks have different orientations with respect to the caustics
crossed.  The slight degradation of the fit can be understood as
follows.  The source track will not, in general, be normal to the
caustic, but will instead have a non-normal velocity component.  If
the caustic is perfectly straight, the velocity component along the
caustic makes no difference.  (Hence our model only considers only the
normal velocity component $v_p$).  But in fact the caustics, although
clean folds do have some curvature.  The combination of a curving
caustic and non-normal velocity of the source makes the orientation of
the source twist with respect to the caustic.  This twist would be
different for crossings along the AB and CB tracks.
